Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A cross-sectional study based on the parametric g-formula

### 2024-08-12 output/paper/manuscript.qmd
Preparing for submission to Environmental Research.

format:
  docx:
    reference-doc: custom-reference-doc.docx

@@

bibliography: bibliography.bib
csl: epidemiology.csl

@@

acronyms:
  fromfile: acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical

@@

@@

# Methods {#sec-methods}

@@

@@

>>>>

format:
  docx:
    reference-doc: custom-reference-doc.docx
    fig-dpi: 420

@@

bibliography: bibliography.bib
csl: environmental-research.csl

@@

acronyms:
  fromfile: acronyms.yml
  insert_links: false
  insert_loa: false
  include_unused: true
  loa_title: ""
  sorting: alphabetical

@@

# List of Acronyms {.unnumbered}

\printacronyms

@@

# Material and methods {#sec-methods}

@@

## Conclusion

@@

# Acknowledgments

The authors acknowledge that Born in Bradford is only possible because of the enthusiasm and commitment of the children and parents in Born in Bradford. We are grateful to all participants, health professionals and researchers who have made Born in Bradford happen.

The authors thank the EDEN mother-child cohort study group, whose members are I. Annesi-Maesano, J.Y. Bernard, M.A. Charles, P. Dargent-Molina, B. de Lauzon-Guillain, P. Ducimetière, M. de Agostini, B. Foliguet, A. Forhan, X. Fritel, A. Germa, V. Goua, R. Hankard, B. Heude, M. Kaminski, B. Larroquey, N. Lelong, J. Lepeule, G. Magnin, L. Marchand, C. Nabet, F Pierre, R. Slama, M.J. Saurel-Cubizolles, M. Schweitzer, and O. Thiebaugeorges.

### 2024-08-12 output/paper/title_page.qmd
Preparing for submission to Environmental Research.

embed-resources: true
format:
  html: default

@@

## Acknowledgments

The authors acknowledge that Born in Bradford is only possible because of the enthusiasm and commitment of the children and parents in Born in Bradford. We are grateful to all participants, health professionals and researchers who have made Born in Bradford happen.

The authors thank the EDEN mother-child cohort study group, whose members are I. Annesi-Maesano, J.Y. Bernard, M.A. Charles, P. Dargent-Molina, B. de Lauzon-Guillain, P. Ducimetière, M. de Agostini, B. Foliguet, A. Forhan, X. Fritel, A. Germa, V. Goua, R. Hankard, B. Heude, M. Kaminski, B. Larroquey, N. Lelong, J. Lepeule, G. Magnin, L. Marchand, C. Nabet, F Pierre, R. Slama, M.J. Saurel-Cubizolles, M. Schweitzer, and O. Thiebaugeorges.

>>>>

embed-resources: true
format:
  docx: default

filters:
  - authors-block

@@
